---
title: "Exploring phage networks"
author: "Sasha Mikheyev"
date: "8/10/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse) # various useful R enhancenents
library(bipartite) # for network tools
```

## Bipartite library exporation

We'll go though some relevant elements of the [bipartite vignette](https://cran.r-project.org/web/packages/bipartite/vignettes/Intro2bipartite.pdf)

```{r bipartite}
plotweb(motten1982)
visweb(motten1982)
mod <- computeModules(motten1982)
plotModuleWeb(mod)
```

# Network-level statistics

```{r}
networklevel(bezerra2009, index=c("ISA", "NODF", "Fisher alpha"), SAmethod="log")
```

## Modularity
`computeModules` produces a specific data class. You can find documentation on the data class returned by computeModules [here](https://www.rdocumentation.org/packages/bipartite/versions/2.15/topics/moduleWeb-class).
- it contains a `likelihood` parameter, which is the extent of modularity  

```{r modularity}
mod <- computeModules(motten1982)
plotModuleWeb(mod)
```

Testing whether modularity in this data set is higher than expected by chance. Note: `N` is set low, for speed. If you want to trust these results, you would have to increase it to 1000 or more.

```{r module_nullmodel}
nulls <- nullmodel(motten1982, N=100, method="r2d")
Inulls <- pbapply::pbsapply(nulls, function(x) computeModules(x)@likelihood) 
ggplot(data.frame(Q = Inulls), aes(Q)) + geom_density() + geom_vline(xintercept = mod@likelihood, color = "red") + xlim(0,1)
```

### Random thoughts
-  potential for apparent competition function may be relevant to phage-bacterial interactions
