---
title: "Flores et al"
author: "Sasha Mikheyev"
date: "8/10/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse) # various useful R enhancenents
library(readxl) # for reading excel files
library(bipartite) # for network tools
```

## Flores et al

Read raw data from the excel file. There are separate sheets for each experiment, and we load all of them into a list, where each element is a matrix.

```{r load_Flores_data}
studies <- excel_sheets("data/sd02.xls")
phageDat <- lapply(studies, function(x) read_excel("data/sd02.xls", sheet = x))
names(phageDat) <- studies
```

## Getting started

- What was indixes were analyzed in the original paper?

The details of the methods are in the [online supplement](https://www.pnas.org/content/pnas/suppl/2011/06/24/1101595108.DCSupplemental/sapp.pdf). 
- They used the Q metric 

## Examining nestedness in the data set

- Note: I'm using 100 permutations for speed, in reality you would want something like 1000.
- To speed things up I pre-computed a couple of the variables. The `readRDS` and `loadRDS` commands just check to see if pre-computed results exist and load them, if need be.

```{r nestedness}
if (file.exists("nulls.RData")) {
  nulls <- readRDS("nulls.RData")
} else { 
  nulls <- lapply(phageDat, function(x) nullmodel(x, N=100, method="shuffle.web"))
  saveRDS(nulls, "nulls.RData")
}

nestednessObs <- sapply(phageDat, function(x) networklevel(x, index="nestedness"))

if (file.exists("nestednessNulls.Rdata")) {
  nestednessNulls <- readRDS("nestednessNulls.RData")
} else { 
  nestednessNulls <- pbapply::pblapply(nulls, function (x) sapply(x, function(y) networklevel(y, index="nestedness")))
  saveRDS(nestednessNulls, "nestednessNulls.RData")
}
```

## Examining output

We'll try to make something like Fig. 6B.

```{r}
nestednessDat <- data.frame(mean = sapply(nestednessNulls, function(x) mean(x)),
           lower = sapply(nestednessNulls, function(x) quantile(x, 0.025, na.rm = T)),
           upper = sapply(nestednessNulls, function(x) quantile(x, 0.975, na.rm = T)),
           observed = nestednessObs,
           study = studies)
nestednessDat$study <- factor(nestednessDat$study, levels = studies[order(nestednessDat$mean)])

ggplot(nestednessDat, aes(x = study, y = observed)) + geom_point(color = "red") + geom_point(aes(y = mean), color = "black") + geom_errorbar(aes(ymin = lower, ymax = upper, width = 0.2)) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

On the whole, we're getting similar results, in that networks seem slightly more nested than observed. The results don't quite match up, since I don't think we're using the same kind of null model and the same nestedness statistic, but overall similar

## Homework

- Recreate Fig. 6A.
- According to Delmas et al NODF is currently the most commonly used nestedness measure. Does using it affect the results?
- Do you get the same results if you use a different network permutation approach? Here I used the `shuffle.web` algorithm, but `mgen` should also work for binary networks. You can find more information about there algorithms by examining the function documentation, e.g., `?shuffle.web`
- Do we need addtional null models for our study?

